Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-30 Ben_Manuscripts/transport/Supporting_Information.tex
Revisions after full read-through

\title{Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \texttt{/setup/param.sh} & TBD & Parameterize liquid crystal monomers and 
  solutes with GAFF \\ \hline

  \texttt{/setup/solvation\_equilibration.py} & TBD & Add water to the pores and tails
  in order to achieve a specific total water content and ratio of water molecules in each
  region, then equilibrate the solvated system. \\ \hline

  \texttt{/setup/input.py} & TBD & Create GROMACS topology and .mdp files \\ \hline

  \texttt{/setup/xlink.py} & TBD & Iteratively cross-link a configuration \\ \hline

  \texttt{/setup/place\_solutes\_pores.py} & TBD & Place a desired number of solutes
  in the pore center, equally space in the $z$-direction. \\ \hline

  \texttt{/analysis/msd.py} & TBD & Calculate the mean squared displacement of residues \\ \hline

  \texttt{/analysis/rdf.py} & TBD & Calculate the cylindrical radial distribution function of
  a solute or membrane component with respect to the pore centers. \\ \hline

  \texttt{/analysis/hbonds.py} & TBD & Identify hydrogen bonds based on geometric criteria \\ \hline

  \texttt{/timeseries/forecast\_ctrw.py} & TBD & Construct dwell time and hop length distributions \\ \hline

  \texttt{/analysis/coordination\_number.py} & TBD & Calculate number of molecules or atoms within a
  cutoff distance of another type of molecule or atom. \\ \hline

  \texttt{/analysis/ztrace.py} & TBD & Plot the center of mass $z$-coordinate of an atom or molecule
  versus time which is colored according to its distance from the pore center. \\ \hline

@@

  We initially attempted to equilibrate our system with water by allowing water
  molecules to naturally penetrate the membrane from a water bath separating
  periodic images of the system in the $z$-direction (See Figure~\ref{fig:gap}).
  We allowed a dry, previously equilibrated system to further equilibrate in
  coexistence with a 3 nm-thick (in the $z$-direction) layer of water. Water
  readily enters the tail region where the density of monomers is low. About 3
  times more water molecules occupy the tail region after 1000 ns of
  equilibration (See Figure~\ref{fig:equilibrated_water_penetration}). Although
  the water level in the pore appears to plateau in this system, it is clear that
  equilibration of this system is kinetically limited since water does not fill
  the pores uniformly. The density of water along the pore axis, averaged over
  the last 50 nanoseconds of simulation, is close to zero at the membrane center.
  Therefore, we required a different equilibration technique in order to overcome
  the kinetic limitation.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.18\textwidth}
  \includegraphics[width=\linewidth]{gap.pdf}
  \caption{}\label{fig:gap}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with : solute_partitioning.py -t shifted.xtc -g berendsen.gro -buffer 2 -r SOL
% in directory : /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/gaps/pre_equilibrated
  \includegraphics[width=\linewidth]{equilibrated_water_penetration.pdf}
  \caption{}\label{fig:equilibrated_water_penetration}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with custom script density.py located in same directory as above.
  \includegraphics[width=\linewidth]{penetration_density.pdf}
  \caption{}\label{fig:penetration_density}
  \end{subfigure}  
  \caption{(a) Using an equilibrated dry configuration, we inserted a layer of water between
           periodic copies of the system in the $z$-direction. (b) Water slowly enters 
	   the membrane. Most water enters the tail region where the density of monomers is
	   lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
	   content of the pore appears equilibrated in (b), the density of water throughout
	   the pores is not uniform, with almost no water close to the pore center. Note that
           the density is not shown below 3 nm or above 9.5 nm, because the the system
	   enters the water layer at those points.
  }\label{fig:gap_solvation}
  \end{figure}

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails in addition to a water reservoir between periodic images. We filled
  the pores with water by running \texttt{gmx solvate} on our initial
  configuration and removing any water molecules placed outside of the pore
  region. The GROMACS command \texttt{gmx solvate} places water molecules in
  proximity to other atoms based on their van der waals radii and therefore does
  a decent job of preventing equilibration issues. This also means that the
  intial pore radius dictates the water content of the pore. We can however, put
  arbitrary amounts of water into the tail region. We chose to test systems with
  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
  given in Table~\ref{table:water_content}.

@@

@@

  We chose to model 6 solutes in each pore because there was a low degree of 
  interaction between solutes which gave us a sufficient number of independent 
  trajectories to observe and analyze. There are a negligible number of occurrences
  % BJC: not sure what the appropriate cut-off should be
  where the center of a given solute came within 3.5 \AA of another same-solute
  center of mass.

@@

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{fig:se_intersection_sensitivity}
%  \end{figure}

  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}

@@

  \section{Pore Region Definition}\label{section:pore-region}

  We performed a sensitivity analysis in order to determine the radial 
  cut-off that maximizes the difference in hop lengths in and out of 
  the pore region. We varied the location of the cut-off defining the
  edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
  varied the cut-off in increments of 0.1 from 0.7 to 0.8 in order to
  increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
  Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.1 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{fig:pore_cutoff}
  \end{figure}

  \section{Pore Splines}\label{section:splines}

@@

  We calculated the tortuosity, $\tau$, of the pores by calculating the 
  ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
  the length of the unit cell in the $z$-direction.

  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}

  In Section~\ref{M-method:hbonds} of the main text, we established geometric criteria for the 
  identification of hydrogen bond interactions. Namely, if the distance between the donor,
  D, and acceptor, A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less
  than 30\degree, then we consider the interaction to be a consequence of hydrogen bonding.

  We tested the sensitivity of this criteria to ensure that our conclusions
  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}
  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
  angle cut-off between 25 and 35 \degree.

  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}. 
  \begin{enumerate}
    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
    interactions.
    \item The number of multiple-hydrogen-bond interactions increases.
    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
  \end{enumerate}

  \section{Total Membrane Density}\label{section:total_density}

@@

  \section{Solute Pairing with Sodium}

  \begin{figure}[!htb]
  \centering
  %MRS2: would be better if this was paired with ensemble data, instead of just one trajectory.
  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
  the majority of the trapping occurence between 400 and 600 ns. Regions
  highlighted red or blue indicate times when methanol's oxygen atom is within 
  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
  \end{figure}

  %BJC: could probably safely remove this figure
  \section{Mercaptoethanol's range of behavior}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{SOH_trace.pdf}
  \caption{}\label{fig:SOH_trace}
  \end{subfigure}
  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
  to lengthy trapping. Large hops generally occur near the pore center while 
  long entrapments occur while tangled among the monomer tails.}
  \end{figure}

  \section{THF-sodium Complexation}

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
  \caption{Coordination of THF with sodium ions may help stabilize it inside the
  pore region. For the first 700 ns of the trajectories shown, the center of mass
  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
  After 700 ns, THF separates from the sodium ion and moves closer to the head group
  region.}\label{fig:thf_sodium_coordination}
  \end{figure}
  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
  %this is physical or a force field artifact.
  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
  % solutes that we studied

@@

  \clearpage
  \bibliography{transport}

>>>>

\title{Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \texttt{/setup/param.sh} & 2.1 & Parameterize liquid 
  crystal monomers and solutes with GAFF \\ \hline

  \texttt{/setup/solvation\_equilibration.py} & 2.2 & Add water to the pores and tails
  in order to achieve a specific total water content and ratio of water molecules in each
  region, then equilibrate the solvated system. \\ \hline

  \texttt{/setup/input.py} & 2.2 & Create GROMACS topology and .mdp files \\ \hline

  \texttt{/setup/xlink.py} & 2.2 & Iteratively cross-link a configuration \\ \hline

  \texttt{/setup/place\_solutes\_pores.py} & 2.2 & Place a desired number of solutes
  in the pore center, equally space in the $z$-direction. \\ \hline

  \texttt{/analysis/msd.py} & 2.3 & Calculate the mean squared displacement of residues \\ \hline

  \texttt{/analysis/radius.py} & 2.4 & Calculate the maximum end-to-end distance of a solute over a trajectory \\ \hline

  \texttt{/timeseries/forecast\_ctrw.py} & 2.6 & Construct dwell time and hop length distributions \\ \hline

  \texttt{/analysis/rdf.py} & 2.7, 2.11 & Calculate the cylindrical radial distribution function of
  a solute or membrane component with respect to the pore centers. \\ \hline

  \texttt{/analysis/hbonds.py} & 2.8 & Identify hydrogen bonds based on geometric criteria \\ \hline

  \texttt{/analysis/coordination\_number.py} & 2.9 & Calculate number of molecules or atoms within a
  cutoff distance of another type of molecule or atom. \\ \hline

  \texttt{/analysis/lifetime.py} & 2.10 & Calculate association lifetimes \\ \hline

  \texttt{/analysis/ztrace.py} & 3.2.2 & Plot the center of mass $z$-coordinate of an atom or molecule
  versus time which is colored according to its distance from the pore center. \\ \hline

@@

  We initially attempted to equilibrate our system with water by allowing water
  molecules to naturally penetrate the membrane from a water bath separating
  periodic images of the system in the $z$-direction (see Figure~\ref{fig:gap}).
  We allowed a dry, previously equilibrated system to further equilibrate in
  coexistence with a 3 nm-thick (in the $z$-direction) layer of water. Water
  readily enters the tail region where the density of monomers is low. About 3
  times more water molecules occupy the tail region after 1000 ns of
  equilibration (see Figure~\ref{fig:equilibrated_water_penetration}). Although
  the water level in the pore appears to plateau in this system, it is clear that
  equilibration of this system is kinetically limited since water does not fill
  the pores uniformly (see Figure~\ref{fig:penetration_density}). The density of
  water along the pore axis, averaged over the last 50 nanoseconds of simulation,
  is close to zero at the membrane center. Therefore, we required a different
  equilibration technique in order to overcome the kinetic limitation.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.18\textwidth}
  \includegraphics[width=\linewidth]{gap.pdf}
  \caption{}\label{fig:gap}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with : solute_partitioning.py -t shifted.xtc -g berendsen.gro -buffer 2 -r SOL
% in directory : /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/gaps/pre_equilibrated
  \includegraphics[width=\linewidth]{equilibrated_water_penetration.pdf}
  \caption{}\label{fig:equilibrated_water_penetration}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with custom script density.py located in same directory as above.
  \includegraphics[width=\linewidth]{penetration_density.pdf}
  \caption{}\label{fig:penetration_density}
  \end{subfigure}  
  \caption{(a) Using an equilibrated dry configuration, we inserted a 3 nm thick layer 
  of water between periodic copies of the system in the $z$-direction. (b) Water slowly
  enters the membrane. Most water enters the tail region where the density of monomers
  is lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
  content of the pore appears equilibrated in (b), the density of water throughout
  the pores is not uniform, with almost no water close to the pore center. Note that
  the density is not shown below 3 nm or above 9.5 nm, because the the system
  enters the water layer at those points.
  }\label{fig:gap_solvation}
  \end{figure}

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails in addition to a water reservoir between periodic images. We filled
  the pores with water by running \texttt{gmx solvate} on our initial
  configuration and removing any water molecules placed in the tail region. The
  GROMACS command \texttt{gmx solvate} places water molecules in proximity to
  other atoms based on their van der waals radii and therefore does
  a decent job of preventing equilibration issues. This also means that the
  intial pore radius dictates the water content of the pore. We can however, put
  arbitrary amounts of water into the tail region. We chose to test systems with
  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
  given in Table~\ref{table:water_content}.

@@

  \clearpage

@@

  We chose to model 6 solutes in each pore because there was a low degree of 
  interaction between solutes which gave us a sufficient number of independent 
  trajectories to observe and analyze. There are a negligible number of occurrences
  % BJC: not sure what the appropriate cut-off should be
  where the center of a given solute came within 3.5 \AA~of another same-solute
  center of mass.

@@

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{fig:se_intersection_sensitivity}
%  \end{figure}
  \clearpage
  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}

@@

  \clearpage
  \section{Pore Region Definition}\label{section:pore-region}

  We performed a sensitivity analysis in order to determine the radial 
  cut-off that maximizes the difference in hop lengths in and out of 
  the pore region. We varied the location of the cut-off defining the
  edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
  varied the cut-off in increments of 0.01 from 0.7 to 0.8 in order to
  increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
  Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{fig:pore_cutoff}
  \end{figure}

  \clearpage
  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}

  In Section 2.8 of the main text, we established geometric criteria for the 
  identification of hydrogen bond interactions. Namely, if the distance between the donor,
  D, and acceptor, A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less
  than 30\degree, then we consider the interaction to be a consequence of hydrogen bonding.

  We tested the sensitivity of this criteria to ensure that our conclusions
  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}c
  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
  angle cut-off between 25 and 35 \degree.

  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}:
  \begin{enumerate}
    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
    interactions.
    \item The number of multiple-hydrogen-bond interactions increases.
    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
  \end{enumerate}

  \section{Lifetime Distributions}\label{section:lifetime_distributions}

  The distribution of hydrogen bond lifetimes and association lifetimes
  for all solutes appears to be power law or exponentially distributed. 
  Example distributions generated from ethylene glycol are shown in
  Figure~\ref{fig:lifetime_distributions}.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{gcl_hbond_dist.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{gcl_coord_dist.png}
  \caption{}
  \end{subfigure}
  \caption{The distribution of hydrogen bond lifetimes and association lifetimes of
  ethylene glycol both appear to be power law or exponentially distributed. We
  do not attempt to distinguish between the type of distribution and instead report
  the 95\% confidence interval of association lifetimes.}\label{fig:lifetime_distributions}
  \end{figure}

  \clearpage
  \section{Pore Splines}\label{section:splines}

@@

  We calculated the tortuosity, $\tau$, of the pores by calculating the 
  ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
  the length of the unit cell in the $z$-direction. The average tortuosity
  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt\%
  water systems respectively.

  \clearpage
  \section{Total Membrane Density}\label{section:total_density}

@@

%  \clearpage
%  \section{Solute Pairing with Sodium}
%
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
%  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
%  the majority of the trapping occurence between 400 and 600 ns. Regions
%  highlighted red or blue indicate times when methanol's oxygen atom is within 
%  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
%  \end{figure}
%  
%  \section{Mercaptoethanol's range of behavior}
%  
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\linewidth]{SOH_trace.pdf}
%  \caption{}\label{fig:SOH_trace}
%  \end{subfigure}
%  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
%  to lengthy trapping. Large hops generally occur near the pore center while 
%  long entrapments occur while tangled among the monomer tails.}
%  \end{figure}
%  
%  \section{THF-sodium Complexation}
%  
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
%  \caption{Coordination of THF with sodium ions may help stabilize it inside the
%  pore region. For the first 700 ns of the trajectories shown, the center of mass
%  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
%  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
%  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
%  After 700 ns, THF separates from the sodium ion and moves closer to the head group
%  region.}\label{fig:thf_sodium_coordination}
%  \end{figure}
  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
  %this is physical or a force field artifact.
  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
  % solutes that we studied

@@

%  \clearpage
%  \bibliography{transport}
